---
title: CV
name: Indigo
surname: Bannister
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::markdowncv:
    theme: kjhealy
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```


## Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Master of Environmental Science & Management", "Expected 2021", "Bren School of Environmental Science & Management, UC Santa Barbara", "Santa Barbara, CA",
  "B.S. Environmental Management & Protection", "2016", "California Polytechnic State University", "San Luis Obispo, CA"
) %>% 
  detailed_entries(Degree, Year, Where, Institution)
```

## Master's Group Project
```{r}
tribble(
  ~ Company, ~ Year, ~ Title, ~ Where,
  "Locating prescribed fire to maximize water quality benefadits in the Sierra Nevada", "4/20-Present", "Project Manager", "Client: American Rivers"
) %>% 
  detailed_entries(Company, Year, Where, Title)

```

-	Built a fire- and erosion-modeling framework to recommend prescribed fire locations within Central Sierra Nevada watersheds that reduce post-fire erosion loss and protect riparian habitats and water infrastructure.
-	Co-managed a remotely distanced 5-person team which included facilitating team meetings, designing and implementing project management software, and collaborating to meet project objectives.


## Conservation Planning Experience

```{r}
tribble(
  ~ Company, ~ Year, ~ Title, ~ Where,
  "USGS Climate Adaptation Science Center (CASC)", "7/20-9/20", "State Wildlife Action Plan Intern", "Remote"
) %>% 
  detailed_entries(Company, Year, Where, Title)

```

- Created and applied a literature-informed typology system to qualitatively analyze the inclusion of climate adaptation planning in 7 existing State Wildlife Action Plans (SWAP) to guide future CASC support and plans.
-	Developed interview framework to guide future conversations with state wildlife agency representatives.
-	Facilitated a national conversation between regional CASCs about how the network could support SWAPs.

```{r}
tribble(
  ~ Company, ~ Year, ~ Title, ~ Where,
  "Sonoma County Ag + Open Space", "6/17-8/19", "Conservation Planning Technician", "Santa Rosa, CA"
) %>% 
  detailed_entries(Company, Year, Where, Title)

```

-	Coordinated over 180 individuals from 80 organizations in collaboration with superiors to develop the Living in a Fire Adapted Landscape report in response to the 2017 North Bay fires.
-	Composed content, reviewed and integrated over 4,000 public comments, and organized 7 public meetings in support of the development of the Vital Lands Initiative, a comprehensive land conservation plan.
-	Collaborated with graphic designers to develop two 40+ page reports and 12 public messaging documents in support of the Healthy Lands & Healthy Economies Initiative, an ecosystem service valuation.

```{r}
tribble(
  ~ Company, ~ Year, ~ Title, ~ Where,
  "Greenbelt Alliance", "5/17-6/17", "Sustainable Mapping Intern", "San Francisco, CA"
) %>% 
  detailed_entries(Company, Year, Where, Title)

```

-	Calculated park-deficient acres in Santa Rosa and recommended areas for equitable park investment.
-	Analyzed urban park accessibility in the San Francisco Bay Area using ArcGIS to support community planning advocacy aimed at improving quality of life for marginalized communities.




## Additional Environmental Experience

```{r}
tribble(
  ~ Company, ~ Year, ~ Title, ~ Where,
  "Santa Cruz Island Reserve", "3/20-10/20", "Strategic Planning Assistant", "Santa Barbara, CA",
  "Natural Resource Dept., Cal Poly", "10/15–6/16", "LCA Research Assistant", "San Luis Obispo, CA",
  "Sonoma County Ag + Open Space", "6/15-9/15", "Conservation Planning Intern", "Santa Rosa, CA",
  "Sonoma Ecology Center", "6/14-9/14", "GIS Intern", "Glen Ellen, CA"
) %>% 
  detailed_entries(Company, Year, Where, Title)

```

